Technical Report

### 2017-11-28 fully-abstract-comp/technical-report.tex
added the retptr code case and fixed some typos. Added the standard static region definition. More typos.

\[
  \lrr(R)(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : \RegName \fun \World \ldotp \\
      \quad W = \bigoplus_{r \in \RegName} S(r) \\
      \quad \forall r \in \RegName \setminus (\{\pcreg \} \cup R)\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrv(S(r))
    \end{array}
            \right\}
\]
Where $S\text{ is a separation of $W$}$ means that no two partition share the same ``spatial'' region (whatever that is).
\lau{TODO: Rewrite the other definitions to pass around $H_\sigma$ (if this is how we want to handle seals.)}
\[
  \lrv(H_\sigma,W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrc(\sigma,\_)},\\\sealed{\sigma,\vsc_C}\endarray\right)} \;\middle| \;
    \begin{array}{l}
%      \forall n'<n, W' \pubft W, W_\lrv \npair[n']{\stpair[.]{\retptrd(\sigma,\_)}{\sealed{\sigma,\vsc_D}}} \in \lrv(W_\lrv) \ldotp\\
%      \npair[n']{\retptrc(\sigma,\_),\retptrd(\sigma,\_),\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W' \oplus W_\lrv)
    \end{array}
    \right\}\cup\\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrd(\sigma,\baddr,\eaddr)},\\\sealed{\sigma,\vsc_D}\endarray\right)} \;\middle| \;
    \begin{array}{l}
      \vsc_D = ((\rw,\linear),\baddr,\eaddr,\baddr-1) \wedge\\
      \exists r \in \addressable{\linear,W} \ldotp \\
      \quad  \exists \stpair{\ms}{\ms} \ldotp \\
      \qquad \dom(\ms) = [\baddr, \eaddr] \wedge \stareg{\spao} \nequal W(r) \wedge \\
      \qquad \forall W' \privft W \ldotp \\
      \qquad \quad \exists r' \ldotp W'(r') = W(r) \wedge \exists r'' \ldotp W'(r'') = \stdreg{[\stkb,\aaddr]}{\spao} \ldotp \\
      \qquad \qquad { \color{red} \forall (c, c') \in H_\sigma (\sigma) \ldotp \npair{\src{c,\retptrd(\sigma,\baddr,\eaddr)}, c' , \sealed{\sigma,\vsc_D}} \in \lrk(W') }%\text{\lau{This needs some work - specifically what i c and c' and do we need to seal them?}}

%    \forall n'<n, W' \pubft W, W_\lrv \npair[n']{\stpair[.]{\retptrc(\sigma,\_)}{\sealed{\sigma,\vsc_C}}} \in \lrv(W_\lrv) \ldotp\\
%      \npair[n']{\src{\retptrc(\sigma,\_)},\src{\retptrd(\sigma,\_)},\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W' \oplus W_\lrv)
    \end{array}
    \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\sealed{\sigma,\vsc_S}},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}
      \stpair{\vsc}{\vsc} \in H_\sigma \; \sigma \wedge \\
      \forall \stpair{\vsc'}{\vsc'} \in H_\sigma \; \sigma \ldotp \\
      \quad \npair{\src{\vsc_S},\src{\vsc_S'},\vsc_T,\vsc_T'} \in \lre(W) \wedge \\
      \quad \npair{\src{\vsc_S'},\src{\vsc_S},\vsc_T',\vsc_T} \in \lre(W)
    \end{array}
    \right\}\cup\\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{r l l}
      \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\linear,W}\\
      \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\linear,W}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{r l l }
      \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\lin,W}\\
      \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\lin,W}\\
      \perm = \rwx &\Rightarrow& \npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W}\\
      \perm = \rx &\Rightarrow& \npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W}
    \end{array}

    \right\}
  \end{array}
\]

\subsection{Permission based conditions}
\[
  \addressable{\lin,W} =
  \begin{cases}
    \{ r \mid W(r) = (\normal,\_) \} & \text{if $\lin = \normal$} \\
    \{ r \mid W(r) = (\spatialo,\_) \}  & \text{otherwise (i.e. $\lin = \linear$)} \\
  \end{cases}
\]

\[
  \readCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, W} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad W(r) \nsubeq \iota_{[\baddr',\eaddr']}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.

@@

\[
  \writeCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr)}) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, W} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad W(r) \nsupeq[n-1] \iota_{[\baddr',\eaddr']} \wedge \\
      \qquad W(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.

@@

\subsection{Standard regions}
\label{sec:standard-regions}
Standard region:
\[
  \iota_A \defeq (\normal,*,=,=,H_A)
\]
\lau{02-11-2017: I am not sure whether it should be a $\normal$ region. In previous work $\nsubeq$ ignored the ``view'' which it may also do here, and then then it does not matter which one it is.}
where $H_A$ is defined as follows:
\[
  H_A \; s \; \hat{W} \defeq \left\{ \npair{\ms_S,\ms_T} \middle|
    \begin{array}{l}
      \dom(\ms_S) = \dom(\ms_T) = A \wedge \\
      \forall \aaddr \in A \ldotp \npair[n-1]{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(\xi(\hat{W}))
    \end{array}
  \right\}
\]
\lau{01-11-2017: TODO look into what kind of world separation should happen here.}

>>>>

\[
  \lrr(R)(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : \RegName \fun \World \ldotp \\
      \quad W = \bigoplus_{r \in \RegName} S(r) \\
      \quad \forall r \in \RegName \setminus (\{\pcreg \} \cup R)\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrv(S(r))
    \end{array}
            \right\}
\]
Where $S\text{ is a separation of $W$}$ means that no two partition share the same ``spatial'' region (whatever that is).
\lau{TODO: Rewrite the other definitions to pass around $H_\sigma$ (if this is how we want to handle seals.)}
\[
  \lrv(H_\sigma,W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrc(\sigma,\perm,\lin,\baddr,\eaddr,\aaddr)},\\\sealed{\sigma,\vsc_C}\endarray\right)} \;\middle| \;
    \begin{array}{l}
      \vsc_c = ((\perm,\lin),\baddr,\eaddr,\aaddr) \wedge \\
      \forall (\src{c},c') \in H_\sigma(\sigma) \ldotp \\
      \quad \exists r \in \addressable(\linear,W) \ldotp \\
      \qquad  \exists \stpair{\ms}{\ms} \ldotp \\
      \qquad \quad \dom(\src{\ms_S}) = \dom(\ms_T) = [\pi_\baddr(c), \pi_\eaddr (c)] \wedge \stareg{\spao} \nequal W(r) \wedge \\
      \qquad \qquad \forall W' \privft W \ldotp \\
      \qquad \qquad \quad \exists r', W'(r') = W(r), \exists r'', W'(r'') = \stdreg{[\stkb,\eaddr]}{\spao} \ldotp \\
      \qquad \qquad \qquad { \color{red} \npair{(\src{\retptrc(\sigma,\perm,\lin,\baddr,\eaddr,\aaddr)}, \src{c}, \sealed{\sigma,\vsc_c}, c')}} \in \lrk(W')
    \end{array}
    \right\}\cup\\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrd(\sigma,\baddr,\eaddr)},\\\sealed{\sigma,\vsc_D}\endarray\right)} \;\middle| \;
    \begin{array}{l}
      \vsc_D = ((\rw,\linear),\baddr,\eaddr,\baddr-1) \wedge\\
      \exists r \in \addressable{\linear,W} \ldotp \\
      \quad  \exists \stpair{\ms}{\ms} \ldotp \\
      \qquad \dom(\src{\ms_S}) = \dom(\ms_T) = [\baddr, \eaddr] \wedge \stareg{\spao} \nequal W(r) \wedge \\
      \qquad \forall W' \privft W \ldotp \\
      \qquad \quad \exists r', W'(r') = W(r), \exists r'', W'(r'') = \stdreg{[\stkb,\eaddr]}{\spao} \ldotp \\
      \qquad \qquad { \color{red} \forall (\src{c}, c') \in H_\sigma (\sigma) \ldotp \npair{\src{c,\retptrd(\sigma,\baddr,\eaddr)}, c' , \sealed{\sigma,\vsc_D}} \in \lrk(W') }%\text{\lau{This needs some work - specifically what i c and c' and do we need to seal them?}}

%    \forall n'<n, W' \pubft W, W_\lrv \npair[n']{\stpair[.]{\retptrc(\sigma,\_)}{\sealed{\sigma,\vsc_C}}} \in \lrv(W_\lrv) \ldotp\\
%      \npair[n']{\src{\retptrc(\sigma,\_)},\src{\retptrd(\sigma,\_)},\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W' \oplus W_\lrv)
    \end{array}
    \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\sealed{\sigma,\vsc_S}},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}
      \stpair{\vsc}{\vsc} \in H_\sigma \; \sigma \wedge \\
      \forall \stpair{\vsc'}{\vsc'} \in H_\sigma \; \sigma \ldotp \\
      \quad \npair{\src{\vsc_S},\src{\vsc_S'},\vsc_T,\vsc_T'} \in \lre(W) \wedge \\
      \quad \npair{\src{\vsc_S'},\src{\vsc_S},\vsc_T',\vsc_T} \in \lre(W)
    \end{array}
    \right\}\cup\\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{r l l}
      \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\linear,W}\\
      \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\linear,W}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{r l l }
      \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\lin,W}\\
      \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\lin,W}\\
      \perm = \rwx &\Rightarrow& \npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W}\\
      \perm = \rx &\Rightarrow& \npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W}
    \end{array}
    \right\}
  \end{array}
\]
\lau{28-11-2017: Do we want the execute condition for $\rwx$ is we are doing write xor execute?}

\subsection{Permission based conditions}
\[
  \addressable{\lin,W} =
  \begin{cases}
    \{ r \mid W(r) = (\pure,\_) \} & \text{if $\lin = \normal$} \\
    \{ r \mid W(r) = (\spatialo,\_) \}  & \text{otherwise (i.e. $\lin = \linear$)} \\
  \end{cases}
\]

\[
  \readCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, W} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad W(r) \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.

@@

\[
  \writeCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr)}) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, W} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad W(r) \nsupeq[n-1] \stdreg{[\baddr',\eaddr']}{\pur} \wedge \\
      \qquad W(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.

@@

\subsection{Standard regions}
\label{sec:standard-regions}
Standard region:
\[
  \stdreg{A}{v} \defeq (v,*,=,=,H_A)
\]
for readability, we use $\spao$ short for $\spatialo$, $\spa$ short for $\spatial$, and $\pur$ as short for $\pure$.
\lau{02-11-2017: I am not sure whether it should be a $\normal$ region. In previous work $\nsubeq$ ignored the ``view'' which it may also do here, and then then it does not matter which one it is.}
where $H_A$ is defined as follows:
\[
  H_A \; s \; \hat{W} \defeq \left\{ \npair{\ms_S,\ms_T} \middle|
    \begin{array}{l}
      \dom(\ms_S) = \dom(\ms_T) = A \wedge \\
      \exists S : \dom(\ms_S) \fun \World \ldotp \xi(W) = \uplus_{\aaddr \in \dom(\ms_S)} S(\aaddr) \wedge\\
      \quad \forall \aaddr \in A \ldotp \npair[n-1]{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))
    \end{array}
  \right\}
\]
\lau{01-11-2017: TODO look into what kind of world separation should happen here.}

\[
  \stareg{v} = (v,*,=,=,H^\mathrm{sta}_{\stpair{\ms}{\ms}})
\]
\[
  H^\mathrm{sta}_{\stpair{\ms}{\ms}} = \{ \npair{\stpair{\ms}{\ms}} \}
\]
